% 03-physical.tex - Section 3: Physical Interfaces

\chapter{Physical Interfaces}
\label{sec:physical}

\section{Overview}

The SHL subsystem interfaces with various hardware components through network connections. All monitored and controlled devices communicate via Ethernet using either SNMP or HTTP protocols.

\section{Network Interfaces}

\subsection{Device Network Interfaces}

All monitored devices are connected to the shelter's internal network (typically 172.16.1.x subnet), as summarized in Table~\ref{tab:device-interfaces}.

\begin{table}[h]
    \centering
    \begin{tabular}{llll}
        \toprule
        \textbf{Device Type} & \textbf{Protocol} & \textbf{Port} & \textbf{Notes} \\
        \midrule
        PDUs & SNMP & 161 & Various manufacturers \\
        UPSs & SNMP & 161 & APC, TrippLite \\
        Thermometers & SNMP & 161 & HWg STE, Comet P8510 \\
        EnviroMux & SNMP & 161 & Network Technologies \\
        HVAC Controllers & HTTP & 80 & Bard MC4002, IceQube \\
        WebRelay & HTTP & 80 & Control Relay Solutions \\
        \bottomrule
    \end{tabular}
    \caption{Device Network Interfaces}
    \label{tab:device-interfaces}
\end{table}

\subsection{External Software Interfaces}

\begin{newInVersion}{F}
The SHL subsystem receives data from two external software processes via UDP multicast (Table~\ref{tab:external-interfaces}): the lightning detector (Boltek EFM-100C electric field mill) and the voltage monitor (AC line quality monitoring). See Section~\ref{sec:monitor-control} for details.
\end{newInVersion}

\begin{table}[h]
    \centering
    \begin{tabular}{llll}
        \toprule
        \textbf{Interface} & \textbf{Multicast Address} & \textbf{Port} & \textbf{Source} \\
        \midrule
        Lightning Detector & 224.168.2.9 & 7163 & spinningCan.py \\
        Voltage Monitor & 224.168.2.10 & 7165 & lineMonitor.py \\
        \bottomrule
    \end{tabular}
    \caption{External Software UDP Multicast Interfaces}
    \label{tab:external-interfaces}
\end{table}

\section{Power Interfaces}

\begin{siteNote}
The number of racks and PDUs varies by site. The configuration is defined in the site's \texttt{defaults.json} file under the \texttt{pdus.devices} section. Each device entry specifies the PDU type, IP address, and number of outlets.
\end{siteNote}

\subsection{Supported PDU Types}

The following PDU types are supported:

\begin{itemize}
    \item \textbf{APC}: APC AP7921B Switched Rack PDU (8 outlets)
    \item \textbf{Raritan}: Raritan PX2 Series (8 outlets)
    \item \textbf{Dominion}: Raritan Dominion PX (variable outlets)
    \item \textbf{TrippLite}: TrippLite PDUMH20ATNET (8 outlets)
\end{itemize}

\subsection{Supported UPS Types}

The following UPS types are supported:

\begin{itemize}
    \item \textbf{APCUPS}: APC Smart-UPS with network management card
    \item \textbf{TrippLiteUPS}: TrippLite SmartOnline UPS
\end{itemize}

\section{Environmental Interfaces}

\subsection{Temperature Monitoring}

Temperature sensors are polled via SNMP. Two thermometer types are supported:

\begin{itemize}
    \item \textbf{HWg STE}: HW group STE Ethernet thermometer (up to 2 sensors)
    \item \textbf{Comet}: Comet P8510 Ethernet thermometer (1 sensor)
\end{itemize}

\subsection{Environmental Monitoring System}

\begin{newInVersion}{F}
The Network Technologies E-MINI-LXO EnviroMux system provides integrated monitoring for:
\begin{itemize}
    \item Temperature sensors (up to 2)
    \item Smoke detector
    \item Water/leak sensor
    \item Door open/closed sensor
    \item Airflow sensors
\end{itemize}
\end{newInVersion}

\begin{siteNote}
Not all sites have an EnviroMux installed. When not present, the corresponding MIB entries (SMOKE, WATER, DOOR) will return error messages.
\end{siteNote}

\subsection{Weather Station}

Weather data is obtained from a wview database (SQLite format). The weather station hardware is typically a Davis VantagePro2 with WeatherLink data logger.

Database location: \texttt{/var/wview/archive/wview-archive.sdb} (may vary by site)
